\Title

### 2013-01-25 synmut.tex
Added bootstrap on Pfix

\begin{figure}
\begin{center}
\subfloat{\includegraphics[width=0.9\linewidth]{Shankarappa_fix_loss_dt_times}
\label{fig:fixp1}}\\
\subfloat{\includegraphics[width=0.9\linewidth]{Bunnik2008_fixmid_syn_ShankanonShanka}
\label{fig:fixp2}}
\caption{Left panel: time course of loss and fixation of synonymous mutations
 observed in a frequency interval $\nu_0$. The ultimate fraction of synonymous
 mutations that fix as a function of intermediate frequency $\nu_0$ is the
 fixation probability.  Right panel: fixation probability of derived synonymous
alleles is strongly suppressed in C2-V5 versus other parts of the {\it env}
gene, and of nonsynonymous ones. Data from
Refs.~\cite{shankarappa_consistent_1999, bunnik_autologous_2008}.}
\label{fig:fixp}
\end{center}
\end{figure}

>>>>

\begin{figure}
\begin{center}
\subfloat{\includegraphics[width=0.9\linewidth]{Shankarappa_fix_loss_dt_times}
\label{fig:fixp1}}\\
\subfloat{\includegraphics[width=0.9\linewidth]{Bunnik2008_fixmid_syn_ShankanonShanka}
\label{fig:fixp2}}
\caption{(Panel A) Time course of loss and fixation of synonymous mutations
observed in a frequency interval $\nu_0$. The ultimate fraction of synonymous
mutations that fix as a function of intermediate frequency $\nu_0$ is the
fixation probability. (Panel B) Fixation probability of derived synonymous
alleles is strongly suppressed in C2-V5 versus other parts of the {\it env}
gene. The horizontal error bars on the abscissa are bin sizes, the vertical ones
the standard deviation after 100 patient bootstraps of the data. Data from
Refs.~\cite{shankarappa_consistent_1999, bunnik_autologous_2008}.}
\label{fig:fixp}
\end{center}
\end{figure}
